### 2019-09-20 bp_intro_v3.tex
refocused introduction on stress

%!TEX root = bioPrediction_main.tex
\section{Introduction}
\textit{`The most valuable asset of a 21st-century institution (whether 
business or non-business) will be its knowledge workers and their 
productivity'}~\cite{drucker1999knowledge}. Knowledge workers constantly face 
challenges, such as a high work fragmentation, continuous disruptions and 
distractions, highly complex and demanding tasks, and long working 
hours~\cite{gonzalez2004constant,mark2008cost,czerwinski04diary}. These 
challenges make it difficult for a knowledge worker to stay focused and
impact interaction with their digital environment, the quality of work performed and productivity. For instance, the 
continuous disruptions that knowledge workers face in office work environments 
can lead to a higher error rate and a lower 
performance~\cite{bailey2001effects,mark2008cost}. In some cases,
the consequences are even more severe; e.g., in control room
settings, the consequences of an erroneous intraction can lead to accidents valued in millions of dollars in losses. 
%when a sleepy operator might, for example, miss early warning signs and cause...
%\todo{Nick: can you find a good example here and citation?}. 
%Similarly, stress at the workplace is a growing concern at the workplace and one of the most common work-related health problem that can lead to fatigue, burnout and various other illnesses, resulting in work absence and a high productivity loss~\cite{hockey1997stress,setz2010stress,wrs2010}. 
Less immediate, but just as insidious, stress at the workplace is a growing 
concern and one of the most common work-related health problems. It leads to 
fatigue, burnout and various other illnesses, ultimately resulting in work 
absences and marked productivity 
losses~\cite{hockey1997stress,setz2010stress,wrs2010}.

Being able to continuously measure human aspects --- such as focus, awakeness, 
and stress --- in the workplace bears huge potential for better supporting 
knowledge workers combatting workplace challenges, and improving productivity 
and well-being. Such measures could be used to provide better interaction with 
their environment, such as management 
of disruptions~\cite{iqbal2005effectiveness,zuger2017reducing}, to 
automatically adjust lighting and temperature to reduce sleepiness, or to continuously monitor stress levels to trigger pro-active 
interventions and reduce health problems.

Fortunately, with recent advances in sensing technologies there is increasing 
hope that we can accurately and automatically measure such human aspects. A 
number of HCI studies have discussed and investigated the use of biometrics to 
measure aspects such as a person's cognitive state 
%This change is regarding Reviewer 2's concern: what are the "aspects"?
(e.g., processing load)~\cite{beatty82,Kramer90,richter1998psychophysiological,Rowe98,Wilson2002}, 
and more specifically to measure stress~\cite{dishman2000stress,Setz2010}, 
or awakeness / (energetic) arousal~\cite{exler2016tired,mcduff2012affectaura,haag2004emotion}. Similarly,
studies have examined the occurrence, cause and effect of similar 
aspects in various contexts~\cite{mark2014bored,mark2008cost}, how these can be measured~\cite{Hernandez14}, and 
 how they might be modulated/regulated~\cite{Snyder15}. 
While previous work mostly focused on smaller or controlled lab studies, our study extends this work by performing a field study to examine whether and how these three variables ---stress, focus and awakeness--- can be measured over an extended period of time in a knowledge worker's context, 
%Yet, very few 
%studies measure productivity-related factors in the workplace over an 
%extended period of time
and little is known about measuring the more 
abstract concept of focus (i.e., directed attention). 
% Added regarding concern of Reviewer 2: Define what is meant by focus when it's first introduced. 
Given the importance of focus, described as a 
combination of engagement and challenge in a work task by Mark et al.~\cite{mark2014bored}, to an office workers' productivity, this factor also 
deserves further study.

The objective of our research is to develop continuous (and automatic) 
measures of focus, awakeness, and stress in the workplace. These measures are 
targeted towards improving knowledge workers' productivity and 
well-being in the future by customizing interaction with their environment; e.g., by automatically protecting the workers
from audible interruptions during a high focus period by showering them 
with white noise or by recommending stress-reducing interventions during an 
extended period of high stress.

@@

The results of our analysis show that biometrics of a single minimally invasive sensor can be used to predict productivity-related indicators accurately, with the abstract concept of focus (predictably) being the hardest to detect. The results also show that knowledge workers' self-reported levels of stress, focus and awakeness and their physiological manifestation and prediction can vary a lot between individuals. Our results further show that overall combining biometric features with computer interaction information 
results in an improvement
over each of the training sets individually.
The main contributions of our work are:
\begin{itemize}
	\item The creation and analysis of measures for the automatic monitoring of knowledge workers' awakeness, stress, and focus in the workplace based on an eight-week field study with 14 office workers.
	\item A thorough analysis of ways to increase performance, including the training sample size, time window to collect data, and the inclusion of computer interaction features.
	\item A discussion on the impact of applying this research to improve
the interaction of knowledge workers with their digital environment leading to an improvement in their productivity and well-being, besides a reflection on aspects that can be further improved in future studies.
    \end{itemize}

>>>>

%!TEX root = bioPrediction_main.tex
\section{Introduction}
\textit{`The most valuable asset of a 21st-century institution (whether 
business or non-business) will be its knowledge workers and their 
productivity'}~\cite{drucker1999knowledge}. Knowledge workers constantly face 
challenges, such as a high work fragmentation, continuous disruptions and 
distractions, highly complex and demanding tasks, and long working 
hours~\cite{gonzalez2004constant,mark2008cost,czerwinski04diary}. 
Consequently, stress in the workplace is an ever-growing concern. It leads to 
fatigue, burnout and various other illnesses, ultimately resulting in work 
absences and marked productivity 
losses~\cite{hockey1997stress,setz2010stress,wrs2010}.
But while the effects of stress are obvious the causes can be more subtle. Stress can be caused by
a multitude of factors within the office including but not limited to workload, management issues, workplace harassment and bullying,
constant interruptions, and noisy environments. It could also be the result of external stressors seeping into the workplace.
Regardless of the cause, garnering an understanding of what stress looks like in the workplace could
prove invaluable to helping us develop effective interventions.
Likewise, being able to continuously measure stress in the workplace bears huge potential for better supporting 
knowledge workers in combatting workplace challenges, and improving productivity 
and well-being.

At the same time, these 
challenges that contribute to stress levels can make it hard for knowledge workers to stay focused, impact interaction with their digital environment,degrade the quality of work performed and hinder productivity.
For instance, the continuous disruptions that knowledge workers face in office work environments can lead to a higher error rate and lower 
performance~\cite{bailey2001effects,mark2008cost}.

Fortunately, with recent advances in sensing technologies there is increasing 
hope that we can accurately and automatically measure stress and it's related aspects. A 
number of HCI studies have discussed and investigated the use of biometrics to 
measure aspects such as a person's cognitive state 
%This change is regarding Reviewer 2's concern: what are the "aspects"?
(e.g., processing load)~\cite{beatty82,Kramer90,richter1998psychophysiological,Rowe98,Wilson2002}, 
and more specifically to measure stress~\cite{dishman2000stress,Setz2010}, 
or awakeness / (energetic) arousal~\cite{exler2016tired,mcduff2012affectaura,haag2004emotion}. Similarly,
studies have examined the occurrence, cause and effect of similar 
aspects in various contexts~\cite{mark2014bored,mark2008cost}, how these can be measured~\cite{Hernandez14}, and 
 how they might be modulated/regulated~\cite{Snyder15}. 
While previous work mostly focused on smaller or controlled lab studies, our study extends this work by performing a field study to examine whether and how these three variables ---stress, focus and awakeness--- can be measured over an extended period of time in a knowledge worker's context, 
%Yet, very few 
%studies measure productivity-related factors in the workplace over an 
%extended period of time
and little is known about measuring the more 
abstract concept of focus (i.e., directed attention). 
% Added regarding concern of Reviewer 2: Define what is meant by focus when it's first introduced. 
Given the importance of focus, described as a 
combination of engagement and challenge in a work task by Mark et al.~\cite{mark2014bored}, to an office workers' productivity, this factor also 
deserves further study.

In this research we examine what office stress actually looks like over long periods of time, and develop continuous (and automatic) 
measures of stress, focus, and awakeness in the workplace. These measures are targeted towards improving knowledge workers' productivity and 
well-being in the future by customizing interaction with their environment; e.g., by continuously monitoring stress levels and recommending stress-reducing interventions during 
extended periods of high stress, automatically adjusting lighting and temperature to heighten awakeness, or improving management 
of disruptions~\cite{iqbal2005effectiveness,zuger2017reducing} to aid with focus and productivity.

@@

The results of our analysis show that biometric signals collected from a single minimally invasive sensor can be used to predict stress and its related aspects accurately, with the abstract concept of focus (predictably) being the hardest to detect. The results also show that knowledge workers' self-reported levels of stress, focus and awakeness and their physiological manifestation and prediction can vary a lot between individuals. Our results further show that overall combining biometric features with computer interaction information 
results in an improvement
over each of the training sets individually.
The main contributions of our work are:
\begin{itemize}
	\item An qualitative examination of how knowledge worker stress presents and fluctuates in the wild.
	\item The creation and analysis of measures for the automatic monitoring of knowledge workers' awakeness, stress, and focus in the workplace based on an eight-week field study with 14 office workers.
	%\item A thorough analysis of ways to increase performance, including the training sample size, time window to collect data, and the inclusion of computer interaction features.
	\item A discussion on the impact of applying this research to improve
the interaction of knowledge workers with their digital environment leading to an improvement in their productivity and well-being, besides a reflection on aspects that can be further improved in future studies.
    \end{itemize}
